---
title: "BRMS Testing"
author: "SaferSeafood"
date: "2024-05-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE) 

library(tidyverse)
library(brms)
library(bayesplot)
library(loo)
```

## Overview

---

### The Data

The data used in this project will be:

***Sediment Data***

The sediment .rds file contains the total DDT sediment concentration and year. 

***Fish Data***

Fish life history:
Fish life history data contains trophic and feeding position data for species that were sampled. 

Fish DDT data:
Fish DDT data contains total DDT concentration, lipid normalized DDT data, and other fish DDT information.

### Summary of document

The purpose of this document is to summarize the process of choosing our final model using BRMS. Our task was to update models predicting DDT concentrations in fish (found in client_models.R). The original models used lipid-normalized DDT concentrations for predictions, but our models will use non lipid-normalized DDT concentrations. 
The code is supplemented with text describing what we were testing and the decisions we made. Because this is not just our final model, running the code in this document is not necessary. This is a tool to use to understand the process of creating the updated model. The machine learning testing of the model can be found in the document tidymodels_testing.Rmd within the same folder.

## Highlights

* Load in data
* Run models with non-lipid normalized data
* Compare updated model to original model
* Run same models with family instead of species

*Model name guide*

All models that end with ".non" predict non lipid-normalized DDT tissue concentrations.

The following models are different variations of formula structure that were tested, but were not chosen:

`brm.none.non` 
`brm.habitat.slope.non`
`brm.habitat.intercept.non`
`brm.diet.slope.non`
`brm.diet.intercept.non`
`brm.diet.slope.non`
`brm.diet.intercept.non`
`brm.trophic.non`
`brm.habitat.non`
`brm.diet.habitat.non`
`brm.diet.habitat.year.non`
`brm.diet.habitat.species.non`

This model  is adaptation of original model that uses all predictors, but uses non lipid-normalized data:

`brm.diet.habitat.species.year.non` 

This model is the model that the clients originally used using trophic level, feeding position, year, and normalized sediment DDT as predictors. This model predicts lipid-normalized DDT tissue concentrations:

`brm.diet.habitat.species.year.original` 

--- 

## Code

**Load in data**

This is the data that has been cleaned in the data_cleaning.R script.

```{r}
# load in the cleaned data with non lipid-normalized data
fish_clean <- read_csv(here::here("data", "data_outputs", "ddx_southernCA_norm.csv"))

# load in cleaned data with lipid-normalized data
fish_clean_original <- read_csv(here::here("data", "data_outputs", "ddx_southernCA_lipidnorm.csv"))
```

**Client's final model**

This code contains the client's final model that was created using lipid-normalized data.

The original testing and models used in this project are in client_models.R file.

```{r}
# original model used by client with lipid-nornalized DDT
brm.diet.habitat.species.year.original = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), data = fish_clean_original,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")))
```

**Run models with non-lipid normalized data**

We want to make sure we are testing all the formulas that the client did, so will be testing the client's model formulas the same way that they did, but updated with with non-lipid normalized data rather than lipid-normalized data.

The highest elpd value is the best performing model, in this case it is the model using diet, habitat, species, and year (brm.diet.habitat.species.year.non).

```{r}
# ---- Look at best structure for model ----

brm.none.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans,
               data = fish_clean,
               prior = c(set_prior("cauchy(0, 0.5)",
                                   class = "b")))

brm.habitat.slope.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:feeding_position,
                        data = fish_clean,
                        prior = c(set_prior("cauchy(0, 0.5)",
                                            class = "b")))

brm.habitat.intercept.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + feeding_position,
                            data = fish_clean,
                            prior = c(set_prior("cauchy(0, 0.5)",
                                                class = "b")))

brm.diet.slope.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:trophic_category,
                     data = fish_clean,
                     prior = c(set_prior("cauchy(0, 0.5)",
                                         class = "b")))

brm.diet.intercept.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + trophic_category,
                         data = fish_clean,
                         prior = c(set_prior("cauchy(0, 0.5)",
                                             class = "b")))

brm.trophic.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category,
                  data = fish_clean,
                  prior = c(set_prior("cauchy(0, 0.5)",
                                      class = "b")))

brm.habitat.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * feeding_position,
                  data = fish_clean,
                  prior = c(set_prior("cauchy(0, 0.5)",
                                      class = "b")))

brm.diet.habitat.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position,
                       data = fish_clean,
                       prior = c(set_prior("cauchy(0, 0.5)",
                                           class = "b")))

brm.diet.habitat.year.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year,
                            data = fish_clean,
                            prior = c(set_prior("cauchy(0, 0.5)",
                                                class = "b")))

brm.diet.habitat.species.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position  + (1|CompositeCommonName),
                               data = fish_clean,
                               prior = c(
                                 set_prior("cauchy(0, 0.5)", class = "b"),
                                 set_prior("cauchy(0, 2)", class = "sd")))

brm.diet.habitat.species.year.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName),
                                    data = fish_clean,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")))

# ---- Compare LOOIC ----
LOO.results = LOO(brm.none.non,
                  brm.habitat.slope.non,
                  brm.habitat.non,
                  brm.habitat.intercept.non,
                  brm.diet.slope.non,
                  brm.diet.intercept.non,
                  brm.trophic.non,
                  brm.diet.habitat.non,
                  brm.diet.habitat.year.non,
                  brm.diet.habitat.species.non,
                  brm.diet.habitat.species.year.non)

LOO.results

## Look at paramter estimates for best-fit model (80% highest density credible intervals)
mcmc_intervals_data(brm.diet.habitat.species.year.non, point_est="mean",prob = 0.8, prob_outer = 1)
```

**Compare more models**

Using the best model, we wanted to remove species as a predictor to see if it performs just as well, and will potentially help predictive power if fisherman catch a species not included in our data.

We compared the performance of this model, the client's original model, and the brm.diet.habitat.species.year.non model ran previously.

The performance of the updated model with all predictors is comparable to the original model (determined by elpd and R-squared value). However, when removing species, the performance drops. 

```{r}
# removing species as a predictor
brm.diet.habitat.year.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, data = fish_clean, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")))

# compare results
loo_results <- LOO(brm.diet.habitat.species.year.original, 
                   brm.diet.habitat.species.year.non,
                   brm.diet.habitat.year.non)

loo_results

# look at R2 
R2.results = lapply(X=list(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year.non,
                   brm.diet.habitat.year.non), 
                   FUN=bayes_R2)

R2.results
```

Here, we save the final model we will be using as an .rda file, so we can load it into our dashoard.

```{r}
#saveRDS(brm.diet.habitat.species.year.non, file = here::here("data", "data_outputs", "brm_species_model.rda"))
```

**Run same models with family instead of species**

To continue to understand if we can remove species as a predictor and improve predictive power, we tested the same model, but with family instead of species. 

This model did not perform better than brm.diet.habitat.species.year.non, so we will stick with the first model, which includes the same predictors as the client's model.

```{r}
# brm.diet.habitat.species.year.non but with family instead of species
brm.diet.habitat.year.fam.non = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|Family), 
                                data =fish_clean, # changed data
                                prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")) 
                                    )

# compare results
loo_results <- LOO(brm.diet.habitat.species.year.original, 
                   brm.diet.habitat.species.year.non,
                   brm.diet.habitat.year.fam.non)

loo_results

# r2 values
R2.results = lapply(X=list(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year.non,
                   brm.diet.habitat.year.fam.non), 
                   FUN=bayes_R2)

R2.results
```

**Here is some practice making predictions on new data!**

```{r}
predict(brm.diet.habitat.species.year.non,
              data.frame(TotalDDT.sed.trans = 0.735932630, # get from fishing zone
                   trophic_category = "Secondary Carnivore", # get from life history characteristics
                   feeding_position = "Benthopelagic", # get from life history characteristics
                   CompositeCommonName = "white croaker",
                   Year = 2))
```


## Results/Overview

In this document we ran multiple different model structures for predicting non lipid-normalized DDT predictions. Our best performing model used the same formula as the client's final model using lipid-normalized data. The updated model does not perform just as well as the client's original model, but it performs the best out of all models using non lipid-normalized data.
