---
title: "Tidymodels Testing"
author: "SaferSeafood"
date: "2024-03-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rfishbase)
library(tidyverse)
library(tidymodels)
library(multilevelmod)
library(rstanarm)
```

## Overview

---

### The Data

The data used in this project will be:

***Sediment Data***

The sediment .rds file contains the total DDT sediment concentration and year. 

***Fish Data***

Fish life history:
Fish life history data contains trophic and feeding position data for species that were sampled. 

Fish DDT data:
Fish DDT data contains total DDT concentration, lipid normalized DDT data, and other fish DDT information.

### Summary of document

This document contains model testing using a machine learning approach to test predictive accuracy of our chosen model (updated model with non lipid-normalized data). The decisions to choose a model formula can be found in the BRMS_testing.Rmd file in the same folder.

This document contains code and text describing the testing process. This document does not contain the final model, just the process of testing the model formula using training and testing datasets.

### Highlights

* Read in data/prep

**Modeling Family and Species as Random Effects**
* Create model spec
* Create workflow
* Train model with training data 
* Predict on test data
* Metrics

**Feature selection**
* Running model without interacting predictors

---

## Code

**READ IN DATA/PREP**

```{r}
# READ IN DATA ----
# read in cleaned data
fish_cleaned <- read_csv(here::here("data", "data_outputs", "fish_clean.csv"))

# read in data with family 
fish_clean_fam <- read_csv(here::here("data", "data_outputs", "fish_clean_fam.csv"))

# DATA SPLITTING ---- 
# split new data
fam_split <- initial_split(fish_clean_fam, prop = 0.7)
fam_train <- training(fam_split)
fam_test <- testing(fam_split)

species_split <- initial_split(fish_cleaned, prop = 0.7)
species_train <- training(species_split)
species_test <- testing(species_split)
```

### MODELING FAMILY and SPECIES AS RANDOM EFFECTS

**Create spec**

```{r}
# create spec
brm_fish_spec_fam <- linear_reg() %>% 
  set_engine("stan_glmer", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")
```

**Create workflow**

```{r}
# this is the workflow suggested by multilevelmod 
lmer_wflow <- 
  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, Family)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|Family))

# species workflow
species_wf <-  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, CompositeCommonName)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName))
```

**Train model with training data**

```{r}
# fit family model
brm_fam_fit <- lmer_wflow %>% 
  fit(data = fam_train) 

# fit species model
brm_species_fit <- species_wf %>% 
  fit(data = species_train)
```

**Predict on test data**

```{r}
# prediction for family model ----
# get predictions
test_predict_fam <- predict(brm_fam_fit, fam_test) %>% #get prediction probabilities for test data
  bind_cols(fam_test)

# get prediction interval and add it to the predictions
predict_species_int <- predict(brm_fam_fit, fam_test, type = "pred_int") %>% 
  bind_cols(test_predict_fam)

# prediction for species model ----
test_predict_species <- predict(brm_species_fit, species_test) %>% 
  bind_cols(species_test)

# get prediction interval and add it to the predictions
predict_fam_int <- predict(brm_species_fit, species_test, type = "pred_int") %>% 
  bind_cols(test_predict_fam)
```

**METRICS**

```{r}
randomfam <- metrics(test_predict_fam, truth = TotalDDT.trans.non, estimate = .pred)
randomspecies <- metrics(test_predict_species, truth = TotalDDT.trans.non, estimate = .pred)

randomfam
randomspecies
```

### Feature Selection

**Running model without the interacting predictors**

```{r}
# create spec
submodel_spec <- linear_reg() %>% 
  set_engine("stan_glmer", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")

# this is the workflow suggested by multilevelmod 
submodel_wflow <- 
  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, Family)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans + trophic_category + feeding_position + Year + (1|Family))

# train using the other workflow
submodel_fit <- submodel_wflow %>% 
  fit(data = fam_train) 

# predict using other workflow
submodel_predict <- predict(submodel_fit, fam_test) %>% #get prediction probabilities for test data
  bind_cols(fam_test)

submodel_metrics <- metrics(submodel_predict, truth = TotalDDT.trans.non, estimate = .pred)

submodel_metrics
```

