---
title: "Preliminary Data Visualizations"
author: "Hope Hahn"
date: "2024-01-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load in packages
library(tidyverse)
library(sf)
library(terra)
library(resample)
library(tmap)
library(maptiles)
library(janitor)
library(ggmap)
```

# Read in data

I read in the raster data and DDT fish concentration .csv.

Unsure what the .gri files are, but were not able to read it in with `rast()`.

```{r}
# read in sea sediment raster data as separate rasters
sed_2003 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))
sed_2008 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))
sed_2013 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))
sed_2018 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))

# -------------------------------------------------------------------
# read in fish ddt concentration data
ddt_fish <- read_csv(here::here("data", "fish_data", "totalDDT_fish_SouthernCA.csv"))

# remove na values for ease of future
ddt_fish <- na.omit(ddt_fish)
```

# Data preparation

### Working with fish DDT data first:

I converted ddt fish concentrations to an sf file so I can plot it with the rasters later. I just set the EPSG to 4326 for no specific reason.

```{r}
# convert ddt fish concentrations to sf 
ddt_fish_sf <- st_as_sf(ddt_fish, coords = c("CompositeTargetLongitude", "CompositeTargetLatitude"), crs = st_crs(4326))
```

I also cleaned the names because they were Camel case. I changed it to lower snake case. I did this for the DDT fish data frame as well as the sf file.

```{r}
# clean names
ddt_fish_clean <- ddt_fish %>% 
  clean_names() # change column names to lower snake case

# sf file
ddt_sf_clean <- ddt_fish_sf %>% 
  clean_names() # change column names to lower snake case
```

I thought it might be beneficial to save each year that match the rasters separately just in case we want to plot all rasters separately. I also did this for the sf file.

```{r}
# select years 2003, 2008, 2013, 2018 and save to separate data files
# 2003 fish ddt concentrations
ddt_fish_2003 <- ddt_fish_clean %>% 
  filter(year == 2003)

# 2008 fish ddt concentrations
ddt_fish_2008 <- ddt_fish_clean %>% 
  filter(year == 2008)

# 2013 fish ddt concentrations
ddt_fish_2013 <- ddt_fish_clean %>% 
  filter(year == 2013)

# 2018 fish ddt concentrations
ddt_fish_2018 <- ddt_fish_clean %>% 
  filter(year == 2018)

# -------------------------------------------------------
# select years for sf file 
ddt_sf_2003 <- ddt_sf_clean %>% 
  filter(year == 2003) 

# 2008 fish ddt concentrations
ddt_sf_2008 <- ddt_sf_clean %>% 
  filter(year == 2008)

# 2013 fish ddt concentrations
ddt_sf_2013 <- ddt_sf_clean %>% 
  filter(year == 2013)

# 2018 fish ddt concentrations
ddt_sf_2013 <- ddt_sf_clean %>% 
  filter(year == 2018)
```

### Working with the rasters

I created a raster stack to take a mean between all the rasters to plot, so we could only have one visualization instead of 4.

I then changed the CRS to EPSG 4326 also to match the fish DDT data.

```{r}
# create raster stack
sed_stack <- c(sed_2003,
               sed_2008,
               sed_2013,
               sed_2018)

# get mean from these years
mean_sed_stack <- app(sed_stack, fun = mean)

# now change crs of this to same as rasters
mean_sed_stack <- project(mean_sed_stack, "EPSG:4326")
```

# Visualizing sediment DDT concentration rasters

These are each separate sediment raster maps from each year.

```{r}
# 2003 map
tm_shape(sed_2003) +
  tm_raster() +
  tm_basemap("OpenStreetMap") +
  tm_title("2003 DDT Sediment Concentrations") 

# 2008 map
tm_shape(sed_2008) +
  tm_raster() +
  tm_basemap("OpenStreetMap") +
  tm_title("2008 DDT Sediment Concentrations") 

# 2013 map
tm_shape(sed_2013) +
  tm_raster() +
  tm_basemap("OpenStreetMap") +
  tm_title("2013 DDT Sediment Concentrations") 

# 2018 map
tm_shape(sed_2018) +
  tm_raster() +
  tm_basemap("OpenStreetMap") +
  tm_title("2018 DDT Sediment Concentrations") 
```

# Visualizing fish DDT Concentrations

Just plotted total DDT concentrations over time.

```{r}
# scatterplot of fish DDT concentrations over time
ggplot(ddt_fish_clean) +
  geom_point(aes(x = year, y = total_ddt)) +
  theme_minimal() +
  labs(title = "DDT Concentration in Fish Over Time") 
```

This is a scatterplot of fish DDT concentrations by location.

```{r}
# scatterplot of fish DDT concentration by location.
ggplot(ddt_fish_clean) +
  geom_point(aes(x = composite_target_longitude, y = composite_target_latitude, color = total_ddt)) + theme_minimal() +
  labs(title = "Fish DDT concentration?",
       x = "Longitude",
       y = "Latitude")
```

# Visualize sediment and fish DDT together

### Using ggplot:

To plot the sf file with ggplot, I needed to convert it to a dataframe. I did this using `as.data.frame()`. I plotted the raster and then plotted the points for fish DDT using geom_sf, and then tried with geom_point to see if it was easier to update aesthetics.

***Problems***: The problem that I had was trying to update the aesthetics for colors that changed the points, but not the raster or vice versa. Also, even though I put `fill = total_ddt` in the aesthetics, the points were not colored by total_ddt values :(.

```{r}
# convert to df
sed_df <- as.data.frame(mean_sed_stack, 
                        xy = TRUE)

# first plot using geom_sf
ggplot() +
  geom_raster(data = sed_df, 
              mapping = aes(x = x, 
                            y = y,
                  fill = mean)) + # assign fill
  geom_sf(data = ddt_sf_clean, 
          mapping = aes(color = total_ddt)) + # use color because fill was already used for raster
  scale_fill_gradient(low = "#B4CCD1FF", high = "#4A2C22FF", # color gradient for DDT concentrations in sediment
                      guide = "legend", breaks = c(100, 200, 1000, 1500, 2000, 2500, 3000)) + 
  scale_color_gradient(low = "#FFB900FF", high = "#1A2814FF") + # color gradient for points
  theme_minimal() +
  labs(title = "DDT Concentrations", 
       x = "Longitude", 
       y = "Latitude", 
       fill = "Sediment Concentrations",
       color = "Average DDT in tissue \nwet weight (ng/g)") # Average DDT for each composite \nin ng/g tissue wet weight

# second plot using geom_point
ggplot() +
  geom_raster(data = sed_df, 
              mapping = aes(x = x, y = y, fill = mean)) +
  geom_point(data = ddt_fish_clean, 
             mapping = aes(x = composite_target_longitude, 
                           y = composite_target_latitude, fill = total_ddt)) +
  theme_minimal() 
```

### Using Tmap:

I plotted the mean raster with the whole fish DDT file.

***Problems***: I couldn't change the colors for this one as well. The points completely blend into the raster :(.

```{r}
# general mean sed stack and all points
tm_shape(mean_sed_stack) +
  tm_raster() +
  tm_shape(ddt_sf_clean) +
  tm_dots("total_ddt",
          col.scale = tm_scale(values = "slateblue4", "slateblue3", "slateblue2","slateblue1")) +
  tm_basemap("OpenStreetMap") +
  tm_title("DDT Concentrations") 
```
