---
title: "Cleaned tidymodels"
author: "Hope Hahn"
date: "2024-03-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rfishbase)
library(tidyverse)
library(tidymodels)
library(multilevelmod)
```

## <span style="color: grey;">Overview</span>

---

### The Data

The data used in this project will be:

***Sediment Data***

The sediment .rds file contains the total DDT sediment concentration and year. 

***Fish Data***

Fish life history:
Fish life history data contains trophic and feeding position data for species that were sampled. 

Fish DDT data:
Fish DDT data contains total DDT concentration, lipid normalized DDT data, and other fish DDT information.

### Summary of document

This file is for comparing the models using family and species as both fixed and random effects in tidymodels.

## <span style="color: grey;">Code</span>

### READ IN DATA/PREP

```{r}
# read in cleaned data
fish_cleaned <- read_csv(here::here("data", "data_outputs", "fish_clean.csv"))
```

***Add family to the data***

```{r}
# get the unique species names - should be 61
species_name <- unique(fish_cleaned$scientific_name)

# look at the list of species using the names - these are different sizes
species_info <- species(species_list = species_name)

# update the names of the fish to match fishbase
species_name_clean <- as.data.frame(species_name) %>% 
  dplyr::mutate(species_name = case_when(species_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                         species_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                          TRUE ~ species_name))

# look at the taxa of the fish 
taxa <- rfishbase::load_taxa()

# filter the taxa based on name 
taxa_filter <- taxa %>% 
  filter(Species %in% species_name_clean$species_name) %>% 
  dplyr::select(scientific_name = Species, Family, Genus)

fish_clean_fam <- fish_cleaned %>% 
  dplyr::mutate(scientific_name = case_when(scientific_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                            scientific_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                                            TRUE ~ scientific_name)) %>%
  left_join(taxa_filter, by = "scientific_name") %>% 
  dplyr::mutate(Family = ifelse(scientific_name == "Doryteuthis opalescens",
                                "Loliginidae",
                                Family))
```

```{r}
# split new data
fam_split <- initial_split(fish_clean_fam, prop = 0.7)
fam_train <- training(fam_split)
fam_test <- testing(fam_split)

species_split <- initial_split(fish_cleaned, prop = 0.7)
species_train <- training(species_split)
species_test <- testing(species_split)
```

### MODEL WITHOUT RANDOM EFFECTS OR CENSORING

```{r}
# set model specification
brm_fish_spec <- linear_reg() %>% 
  set_engine("stan", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")

# create workflow with species
fixed_species_wf <- workflow() %>% 
  add_model(brm_fish_spec) %>% 
  add_formula(TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + CompositeCommonName)

# create workflow with family
fixed_family_wf <- workflow() %>% 
  add_model(brm_fish_spec) %>% 
  add_formula(TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + Family)

# Train the model (species)
species_fixed_fit <- fixed_species_wf %>% 
  fit(data = species_train) 

# train the model(family)
family_fixed_fit <- fixed_family_wf %>% 
  fit(data = fam_train)

# predictions species
species_fixed_predict <- predict(species_fixed_fit, species_test) %>% #get prediction probabilities for test data
  bind_cols(species_test) #bind to testing column

# predictions family
family_fixed_predict <- predict(family_fixed_fit, fam_test) %>% #get prediction probabilities for test data
  bind_cols(fam_test) #bind to testing column

```

# FAMILY and SPECIES RANDOM EFFECT

```{r}
# create spec
brm_fish_spec_fam <- linear_reg() %>% 
  set_engine("stan_glmer", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")

# this is the workflow suggested by multilevelmod 
lmer_wflow <- 
  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, Family)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|Family))

# species workflow
species_wf <-  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, CompositeCommonName)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName))

# train using the other workflow
brm_fam_fit2 <- lmer_wflow %>% 
  fit(data = fam_train) 

brm_species_fit <- species_wf %>% 
  fit(data = species_train)

# predict using other workflow
test_predict_fam2 <- predict(brm_fam_fit2, fam_test) %>% #get prediction probabilities for test data
  bind_cols(fam_test)

test_predict_species <- predict(brm_species_fit, species_test) %>% 
  bind_cols(species_test)
```

# METRICS
```{r}
fixedspecies <- metrics(species_fixed_predict, truth = TotalDDT.trans.non, estimate = .pred)

fixedfam <- metrics(family_fixed_predict, truth = TotalDDT.trans.non, estimate = .pred)

randomfam <- metrics(test_predict_fam2, truth = TotalDDT.trans.non, estimate = .pred)

randomspecies <- metrics(test_predict_species, truth = TotalDDT.trans.non, estimate = .pred)

randomfam
randomspecies

fixedfam
```


