# Load Packages

```{r message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(tidymodels)
library(caret)
# Load the corrplot package
library(corrplot)
library(sjPlot)
library(rstanarm)

library(sf)
library(terra)
library(leaflet)

# for fishbase
library(rfishbase)

if("pacman" %in% installed.packages() == FALSE){install.packages("pacman")}
pacman::p_load(geojsonR, factoextra,sf,dplyr, ggplot2, maps, fields,raster,
               MuMIn, lubridate, tidyr,ggh4x, lme4,sdmTMB,inlabru,cowplot,marmap,sjPlot, tidyverse, plyr, tidybayes, brms, bayesplot, loo,ggeffects,
               DHARMa)
```

# Set up with clean data

```{r, message = FALSE}
# load in the cleaned data with transformed variables 
fish_clean <- read_csv(here::here("data", "data_outputs", "fish_clean.csv"))

# load in the life hsitory characteristics
fish_lh <- read_csv(here::here("data", "fish_data", "fish_life_history.csv"))

# Read in sediment data 
sediment_summary = readRDS(here::here("data","sediment_data","totalDDX_sediment_zone_summary.rds")) %>%
  dplyr::select(Name, Est.2003, Est.2008, Est.2013, Est.2018) %>% 
  gather(key="Year",value="TotalDDT",Est.2003:Est.2018) %>% 
  dplyr::mutate(Year = case_when(Year == "Est.2003" ~ "2003",
                                 Year == "Est.2008" ~ "2008",
                                 Year == "Est.2013" ~ "2013",
                                 Year == "Est.2018" ~ "2018")) %>% 
  dplyr::group_by(Name, Year) %>%
  dplyr::summarize(TotalDDT.sed = (mean((TotalDDT)))) %>%
  dplyr::ungroup() 


```

```{r}
# Comparing the number of fish in the fish_clean and the fish_lh
fish_clean_names <- as.data.frame(unique(fish_clean$CompositeCommonName)) 

fish_lh_names <- as.data.frame(unique(fish_lh$species)) 

# what fish are in fish_lh that are not in the fish_clean
subset(fish_lh_names, 
       !(fish_lh$species %in% fish_clean$CompositeCommonName))


```

## Exploring length and weight variables
```{r}
# eploring the missing weight and length data 
null_weight_fish <- fish_clean %>% 
  filter(is.na(WeightAvg.g))

null_length_fish <- fish_clean %>% 
  filter(is.na(TLAvgLength.mm))

# names of unique ID's
fish_clean_names <- as.data.frame(unique(fish_clean$CompositeCompositeID)) 

# what fish are in null_weight_fish that are not in the null_length_fish
null_length <- subset(fish_clean_names, 
       !(null_weight_fish$CompositeCompositeID %in% null_length_fish$CompositeCompositeID))

null_length_df <- fish_clean %>% 
  filter(CompositeCompositeID %in% null_length$`unique(fish_clean$CompositeCompositeID)`)

null_w_l <- rbind(null_weight_fish, null_length_df)
```


The life history characteristics of interest are the trophic level, trophic category, and the feeding position.

# Testing different models using Machine learning

## Split the data

```{r}
set.seed(425)
fish_split <- initial_split(fish_clean)
fish_train <- training(fish_split)
fish_test <- testing(fish_split)

```

## Load the models of interest

### Their model with `TotalDDT.trans` variable which is transformed DDT concentrations that have been lipid-normalized. This is the baseline accuracy that we are testing.

```{r}
fish_clean_original <- read_csv(here::here("data", "data_outputs", "fish_clean_ORIGINAL.csv"))

brm.diet.habitat.species.year.original = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                      TotalDDT.sed.trans * feeding_position + Year +
                                      (1|CompositeCommonName), data = fish_clean_original,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")))

# using species 
brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data = fish_clean, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))

# removing species from the model 
brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_clean, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")#,   
                              #set_prior("cauchy(0, 2)", class = "sd"))
                            ))

loo_results <- LOO(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year,
                   brm.diet.habitat.year)

R2.results = lapply(X=list(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year,
                   brm.diet.habitat.year), 
                   FUN=bayes_R2)
R2.results

fish_predict <- predict(brm.diet.habitat.species.year.original,
                        fish_clean_original) %>% 
  bind_cols(fish_clean_original)

accuracy_vec(fish_predict, truth = TotalDDT.trans, estimate = Estimate)

# make predictions
#cvvs <- loo_predict(brm.diet.habitat.species.year.original)

fish_clean_original %>% 
  mutate(prediction = cvvs) %>% 
  ggplot(aes(x = TotalDDT.trans, 
                 y = prediction)) +
  geom_point() +
  geom_smooth(method = "glm")
```

### Prediction values

This will be the body of the function that predicts DDT concentrations using user inputs. Data will be drawn from life history dataframe, as well as possible sources for sediment concentration. /

Questions to consider:

\- How to read the output if the variables are logged?

\- Do we have to transform them so that they make sense?

\- Currently the output is a negative number, this doesn't feel like it makes sense.

\- When collecting samples, were the fish at maturity/ at fishing standard? If this is the case, then we could add a predictor variable of size, since there are laws that limit catch size and could inform DDT concentration.

```{r}
# Example output of specific DDT concentration using the model
predict(brm.diet.habitat.species.year.original, 
        data.frame(CompositeCommonName = "barred sand bass", # grab from df
                   TotalDDT.sed.trans = 0.009889753, # get from fishing zone
                   trophic_category = "Tertiary Carnivore", # get from life history characteristics
                   feeding_position = "Benthopelagic", # get from life history characteristics
                   Year = 2050))

fish_predict <- predict(brm.diet.habitat.species.year.original,
                        fish_test) %>% 
  bind_cols(fish_test)

ggplot(data = fish_predict) +
  geom_point(aes(x = TotalDDT.trans.non, y = Estimate))



```

### Our models with the `TotalDDT.trans.non` variable which is transformed DDT concentration, that has not been lipid normalized.

```{r}

# using species 
brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))

# removing species from the model 
brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_train, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")#,   
                              #set_prior("cauchy(0, 2)", class = "sd"))
                            ))


# with tropic level
brm.diet.habitat.tropic.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + tropic_level + Year, 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b")))

fish_train %>% 
  ggplot(aes(x = tropic_level, y = trophic_category)) +
  geom_point()
```

## Machine Learning Attempt 
```{r}
set.seed(425)
fish_split_o <- initial_split(fish_clean_original)
fish_train_o <- training(fish_split_o)
fish_test_o <- testing(fish_split_o)

fit_stan_glm <- 
  stan_glmer(bf(TotalDDT.trans | cen_paired(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
             TotalDDT.sed.trans * feeding_position + Year +
             (1|CompositeCommonName)), data = fish_train_o, refresh = 0, seed = 505)

```


## Set up cross-validation to test model accuracy

```{r}
summary(brm.diet.habitat.species.year)
bayes_R2(brm.diet.habitat.species.year)
loo(brm.diet.habitat.species.year)

loo(brm.diet.habitat.species.year, 
    brm.diet.habitat.year, 
    brm.diet.habitat.tropic.year)
```

Perforn kfold cross validation on each model, and output the rmse.

```{r}

kf <- kfold(brm.diet.habitat.year, save_fits = TRUE, chains = 1)

# define a loss function
rmse <- function(y, yrep) {
yrep_mean <- colMeans(yrep)
sqrt(mean((yrep_mean - y)^2))
}

kfp <- kfold_predict(kf)
rmse(y = kfp$y, yrep = kfp$yrep)
```

### Select the model that performs the best

## Next steps

1.  We have confirmed the model that predicts the DDT concentration in fish based on life history characteristics
2.  Create function

```{r}
sed_2018 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))
plot(sed_2018)

areas <- readRDS(here::here("data", "fish_data", "pelagic_nearshore_fish_zones.rds"))

ddt_fish <- read_csv(here::here("data", "data_outputs", "fish_clean.csv")) %>%
  na.omit(Co) %>% 
  st_as_sf(coords = c("CompositeTargetLongitude", "CompositeTargetLatitude"), 
           crs = st_crs(areas))


leaflet() %>%  
  setView(lng = -118.7, lat = 33.5, zoom = 7.5) %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addGeoJSON(areas$geometry,
             color = "#CEE0EAFF",
             weight = 2,
             fillOpacity = 0.1,
             layerId = "Hi") %>% 
  addCircleMarkers(data = ddt_fish,
                   radius = ~6,
                   color = "pink",
                   stroke = FALSE, fillOpacity = 0.5)
  
```

# Exploring the {fishbase} package in r

Here is the documentation (link)[https://cran.r-project.org/web/packages/rfishbase/rfishbase.pdf]

Suggestions:
- use scientific name not common name since there are many matches

Compared the differences in the names:
- Embiotica jacksoni			
- Rhinobatos productus			
- Doryteuthis opalescens

Recode them into the names that are included in fishbase 
- I couldn't find a record on the fishpase backage of Doryteuthis opalescens, but it has the family Loliginidae

```{r}

# get the unique species names - should be 61
species_name <- unique(fish_clean$scientific_name)

# look at the list of species using the names - these are different sizes
species_info <- species(species_list = species_name)


# Comparing the number of fish in the fish_clean and the fish_lh
fish_clean_names <- as.data.frame(unique(fish_clean$scientific_name)) %>% 
  mutate(species = `unique(fish_clean$scientific_name)`) %>% 
  dplyr::select('species')

fish_lh_names <- as.data.frame(unique(species_info$Species))

# what fish are in fish_clean_names that are not in the species_info
subset(fish_clean_names, 
       !(fish_clean_names$species %in% species_info$Species))

# Recode them into the names that are included in fishbase 

# update the names of the fish to match fishbase
species_name_clean <- as.data.frame(species_name) %>% 
  dplyr::mutate(species_name = case_when(species_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                         species_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                          TRUE ~ species_name))

# look at the taxa of the fish 
taxa <- rfishbase::load_taxa()

# filter the taxa based on name 
taxa_filter <- taxa %>% 
  filter(Species %in% species_name_clean$species_name) %>% 
  dplyr::select(scientific_name = Species, Family, Genus)

fish_clean_test <- fish_clean %>% 
  left_join(taxa_filter, by = "scientific_name")

species_common_science <- fish_clean_test %>% 
  dplyr::select(CompositeCommonName, scientific_name, Family, trophic_category, feeding_position) %>% 
  distinct()

# save the file as a data output
#write.csv(species_common_science, here::here("data/data_outputs/species_common_science.csv"))
```

Run the same tests on them but have family as a random effect
```{r}

fish_clean_original <- read_csv(here::here("data", "data_outputs", "fish_clean_ORIGINAL.csv"))

# add the family and genus to the dataframe
fish.reg.fam <- fish_clean_original %>% 
  dplyr::mutate(scientific_name = case_when(scientific_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                            scientific_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                                            TRUE ~ scientific_name)) %>%
  left_join(taxa_filter, by = "scientific_name") %>% 
  dplyr::mutate(Family = ifelse(scientific_name == "Doryteuthis opalescens",
                                "Loliginidae",
                                Family))

# add the family and genus to the dataframe
fish.clean.fam <- fish_clean %>% 
  dplyr::mutate(scientific_name = case_when(scientific_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                            scientific_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                                            TRUE ~ scientific_name)) %>%
  left_join(taxa_filter, by = "scientific_name") %>% 
  dplyr::mutate(Family = ifelse(scientific_name == "Doryteuthis opalescens",
                                "Loliginidae",
                                Family))
```

# Run with the Original data that is in `fish.reg.fam`

```{r message = FALSE}
# Look at best structure for model
brm.none.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans, data = fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat.slope.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:feeding_position, data = fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat.intercept.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + feeding_position, data =  fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.slope.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:trophic_category, data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.intercept.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + trophic_category, data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))


brm.trophic.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category,
                  data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * feeding_position,
                  data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                         TotalDDT.sed.trans * feeding_position, data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.year.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                              TotalDDT.sed.trans * feeding_position + Year, data =fish.reg.fam, prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                 TotalDDT.sed.trans * feeding_position + (1|Family), data =fish.reg.fam,
                               prior = c(
                                 set_prior("cauchy(0, 0.5)", class = "b"),
                                 set_prior("cauchy(0, 2)", class = "sd"))
                               )

brm.diet.habitat.year.fam = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                      TotalDDT.sed.trans * feeding_position + Year + (1|Family), data =fish.reg.fam,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd"))
                                    )


```

# Run with the non lipid normalized data that is in `fish.clean.fam`
- updated the variable to TotalDDT.trans.non (for the logged ddt data)
- updated the data to `fish_clean ` and `fish.clean.fam`

```{r message = FALSE}
# Look at best structure for model
brm.none = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans, 
                   data = fish_clean, # changed data
                   prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:feeding_position, 
                            data = fish_clean, # changed data
                            prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + feeding_position, 
                                data = fish_clean, # changd data
                                prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:trophic_category, 
                         data = fish_clean, # changed data
                         prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + trophic_category, 
                             data = fish_clean, # changed data 
                             prior = c(set_prior("cauchy(0, 0.5)", class = "b")))


brm.trophic = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category,
                  data = fish_clean, # changed data
                  prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.habitat = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * feeding_position,
                  data = fish_clean, # changed data 
                  prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.fam = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                         TotalDDT.sed.trans * feeding_position, 
                         data = fish_clean, # changed data
                         prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                              TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_clean, # changed data
                            prior = c(set_prior("cauchy(0, 0.5)", class = "b")))

brm.diet.habitat.fam.clean = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + 
                                   TotalDDT.sed.trans * feeding_position + (1|Family), 
                       data =fish.clean.fam, # changed data
                       prior = c(
                                 set_prior("cauchy(0, 0.5)", class = "b"),
                                 set_prior("cauchy(0, 2)", class = "sd"))
                               )

brm.diet.habitat.year.fam.clean = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                      TotalDDT.sed.trans * feeding_position + Year + (1|Family), 
                                data =fish.clean.fam, # changed data
                                prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")) 
                                    )


```


Then get the R2 values for each of these with this chunk:
```{r}
R2.results = lapply(X=list(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year,
                   brm.diet.habitat.year), 
                   FUN=bayes_R2)
```


To look at the resideuals use this link: https://cran.r-project.org/web/packages/tidybayes/vignettes/tidybayes-residuals.html

To create a loop that does leave one out cross validation but separates the data by group 
- create a list of species `species_name_clean`
- for loop that...
  - removes a species and sets it as the test data from `fish.clean.fam`
  - all other data is saved as the training data
  - runs model on the training data
  - predicts the values on the test data 
  - calculates the RMSE of those values
  - finds the mean RMSE of that round
  - saves that RMSE into an outside dataframe
  - moves onto the next species and does it again
- the output is a dataframe with 61 RMSE values 
- calculate the mean RMSE of those values

```{r}
# list of species names 
species_name_clean[2, 1]

test <- fish.clean.fam %>% 
  filter(scientific_name %in% species_name_clean[i, 1])

train <- fish.clean.fam %>% 
  filter(!scientific_name %in% species_name_clean[i, 1]) # remove the species

# model <- add model here on training data

# predictions <- predict(model, test)

# coef_df <- data.frame( R2 = R2(predictions, test$TotalDDT.trans.non),
                       # RMSE = RMSE(predictions, test$TotalDDT.trans.non),
                       # MAE = MAE(predictions, test$TotalDDT.trans.non))

# coef <- data.frame( group = [i], 
                    # R2 = mean(R2),
                    # RMSE = mean(RMSE),
                    # MAE = mean(MAE))

# define the model
model <- brm_fam_fit2

test <- fish.clean.fam %>% 
  filter(scientific_name %in% species_name_clean[1, 1])

train <- fish.clean.fam %>% 
  filter(!scientific_name %in% species_name_clean[1, 1]) # remove the species

# predict using other workflow
predictions <- predict(model, train) %>% #get prediction probabilities for test data
  bind_cols(train)

library(caret)

# print RMSE, R2 and MAE values
coef_df <- data.frame(estimate = postResample(predictions$.pred, train$TotalDDT.trans.non),
                      groups = 1)
coef_df1 <- data.frame(estimate = postResample(predictions$.pred, train$TotalDDT.trans.non),
                      groups = 2)

df <- rbind(df, coef_df)

```

This for loop creates a dataframe with 61 groups of estimates that basically conduct cross validation on the models by leaving each species out and training then testing the model on that species. 
```{r}

# initialize an empty dataframe
df <- data.frame()


# define the model - this is the one that uses family instead of species
# model <- brm_fam_fit2

for (group in 1:nrow(species_name_clean)) {
  test <- fish.clean.fam %>% 
    filter(scientific_name %in% species_name_clean[group, 1])

  train <- fish.clean.fam %>% 
    filter(!scientific_name %in% species_name_clean[group, 1]) # remove the species
  
  # predict using other workflow
  predictions <- predict(model, train) %>% #get prediction probabilities for test data
    bind_cols(train)
  
  # print RMSE, R2 and MAE values
  coef_df <- data.frame(estimate = postResample(predictions$.pred, train$TotalDDT.trans.non),
                      groups = group)
  
  df <- rbind(df, coef_df)
  
}

df <- rownames_to_column(df)

# makes the data frame of how well the model predicted the values 
df_means <- df %>% 
  mutate(value = gsub('[[:digit:]]+', '', rowname)) %>% 
  dplyr::select(value, estimate) %>%
  dplyr::group_by(value) %>%
  pivot_wider(names_from = value, 
              values_from = estimate) %>% 
  unnest(cols = 1:3) %>% # undo the list of lists 
  summarize_each(mean) %>%  # get the mean values
  mutate(model = quo_name(quo(brm_fam_fit2))) # add the model name



```
# Create a function that calculates how well the models do
```{r}

model_performance <- function(model_name, data_frame) {
  
  # initialize an empty dataframe
  df <- data.frame()
  
  
  # define the model - this is the one that uses family instead of species
  model <- model_name
  
  for (group in 1:nrow(species_name_clean)) {
    test <- data_frame %>% # data frame: either clean or fam
      filter(scientific_name %in% species_name_clean[group, 1])
    
    train <- data_frame %>% 
      filter(!scientific_name %in% species_name_clean[group, 1]) # remove the species
    
    # predict using other workflow
    predictions <- predict(model, train) %>% #get prediction probabilities for test data
      bind_cols(train)
    
    # print RMSE, R2 and MAE values
    coef_df <- data.frame(estimate = postResample(predictions$.pred, train$TotalDDT.trans.non),
                          groups = group)
    
    df <- rbind(df, coef_df)
    
  }
  
  df <- rownames_to_column(df)
  
  # extract the name of the model
  name <- deparse(substitute(model_name))
  
  # makes the data frame of how well the model predicted the values 
  df_means <- df %>% 
    mutate(value = gsub('[[:digit:]]+', '', rowname)) %>% 
    dplyr::select(value, estimate) %>%
    dplyr::group_by(value) %>%
    pivot_wider(names_from = value, 
                values_from = estimate) %>% 
    unnest(cols = 1:3) %>% # undo the list of lists 
    summarize_each(mean) %>%  # get the mean values
    mutate(model = name) # add the model name as a string
  
  return(df_means)
  
}



```



# Get the areas with lat and long points 

```{r}
# I did this above
#areas <- readRDS(here::here("data", "fish_data", "pelagic_nearshore_fish_zones.rds"))
areas_sed <- fish_clean %>% 
  dplyr::select(CompositeStationArea, TotalDDT.sed) %>% 
  dplyr::group_by(CompositeStationArea) %>% 
  summarize(TotalDDT.sed = mean(TotalDDT.sed))

```

Testing the shinydashboard prediction
```{r}

df <- predict(brm.diet.habitat.year.fam.clean,
              data.frame(TotalDDT.sed.trans = 0.735932630, # get from fishing zone
                   trophic_category = "Secondary Carnivore", # get from life history characteristics
                   feeding_position = "Benthopelagic", # get from life history characteristics
                   Family = "Sciaenidae",
                   Year = 2))

saveRDS(brm.diet.habitat.year.fam.clean, file = "/Users/lunacatalan/Documents/dev/capstone/SaferSeafood/data/data_outputs/brm_mod.rda")
```




