---
title: "Hope Model Stuff"
author: "Hope Hahn"
date: "2024-02-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary

In this document, I will run the models that were provided by the client, and work on creating a function in which new covariates can be added with ease.

## The Data

The data used in this project will be:

***Sediment Data***

The sediment .rds file contains the total DDT sediment concentration and year. 

***Fish Data***

Fish life history:
Fish life history data contains trophic and feeding position data for species that were sampled. 

Fish DDT data:
Fish DDT data contains total DDT concentration, lipid normalized DDT data, and other fish DDT information.

## Main Steps
***Client Code***
* Read in and tidy sediment and fish data
* Plot 
* BRMS modeling

***My Code***
* Create function to add new covariate

## Regress fish [DDT] against sediment [DDT]

```{r}
# install and/or load the necessary R packages
if("pacman" %in% installed.packages() == FALSE){install.packages("pacman")}
pacman::p_load(geojsonR, factoextra,sf,dplyr, ggplot2, maps, fields,raster, 
               MuMIn, lubridate, tidyr,ggh4x, lme4,sdmTMB,inlabru,cowplot,marmap,sjPlot, tidyverse, plyr, tidybayes, brms, bayesplot, loo,ggeffects,
               DHARMa)
               #rgeos, INLAutils, DHARMa.helpers)
```

## Load in data and add censoring column

**In these steps, we will read in the data, and combine relevent data. We will add columns of transformed data and add censoring column.

*What is censoring column?*

```{r}
# Read in sediment data 
sediment_summary = readRDS(here::here("data","sediment_data","totalDDX_sediment_zone_summary.rds")) %>%
  dplyr::select(Name, Est.2003, Est.2008, Est.2013, Est.2018) %>% # select relevant columns
  gather(key="Year",value="TotalDDT",Est.2003:Est.2018) %>% # not sure what this does
  dplyr::mutate(Year = case_when(Year == "Est.2003" ~ "2003", # change column names?
                                 Year == "Est.2008" ~ "2008",
                                 Year == "Est.2013" ~ "2013",
                                 Year == "Est.2018" ~ "2018")) %>% 
  dplyr::group_by(Name, Year) %>% 
  dplyr::summarize(TotalDDT.sed = (mean((TotalDDT)))) %>% # summarize by name and year
  dplyr::ungroup() 

# -------------------------------------------------------------

# Read in fish life history 
fish_lh = read.csv(here::here("data","fish_data","fish_life_history.csv")) %>% 
  dplyr::mutate(species = tolower(species)) # lowercase species name

# select the long and latitude
fish_location = read.csv(here::here("data","fish_data","totalDDT_fish_southernCA.csv")) %>% 
  dplyr::select(CompositeCompositeID, CompositeTargetLatitude, CompositeTargetLongitude) 

# -------------------------------------------------------------

# Read in fish data, and join with sediments 
fish_reg = read.csv(here::here("data","fish_data","totalDDX_fish_southernCA.csv")) %>% # Read in fish DDT values 
  # We have sediment data blocked off by 2003, 2008, 2013, and 2018. Figure out what (continous) fish years go with which sediment years. 
  dplyr::mutate(NewYear = case_when(Year %in% c(1995:2005) ~ "2003", 
                                    Year %in% c(2006:2010) ~ "2008", 
                                    Year %in% c(2011:2015) ~ "2013", 
                                    Year %in% c(2016:2022) ~ "2018")) %>% 
  left_join(., fish_location) %>%  # join location into fish data
  left_join(., sediment_summary, by=c("CompositeStationArea"="Name", 
                                      "NewYear"="Year")) %>% # join sediment data
  dplyr::left_join(., fish_lh, by=c("CompositeCommonName"="species")) %>%  # join fish life history
  dplyr::mutate(feeding_position = case_when(feeding_position == "pelagic" ~ "Pelagic", 
                                             feeding_position == "midwater" ~ "Midwater",
                                             feeding_position == "benthopelagic " ~ "Benthopelagic",
                                             feeding_position == "benthic" ~ "Benthic", 
                                             TRUE ~ feeding_position)) %>% 
  dplyr::mutate(feeding_position = factor(feeding_position, levels=c("Pelagic","Midwater","Benthopelagic","Benthic"))) %>% 
  dplyr::mutate(trophic_category = case_when(trophic_category == "herbivore" ~ "Herbivore",
                                             trophic_category == "primary_carnivore" ~ "Primary Carnivore",
                                             trophic_category == "secondary_carnivore" ~ "Secondary Carnivore",
                                             trophic_category == "tertiary_carnivore" ~ "Tertiary Carnivore")) 
  
# Add transformed columns (TotalDDT which is non-lipid normalized for fish)
### first is non-lipid normalized
fish_reg$TotalDDT.trans.non = log(fish_reg$TotalDDT + 1) # add + 1 to account for 0 values
### second is sediment data
fish_reg$TotalDDT.sed.trans = log(fish_reg$TotalDDT.sed + 1) 

# Add censoring for values equal to zero (so value is constrained to fall between zero and MDL)
fish_reg = fish_reg %>% 
   dplyr::mutate(Censored = ifelse(TotalDDT.trans.non == 0, "interval","none"), 
                 Detection.Limit = ifelse(is.na(MDL.min), 
                                          0.5, # if MDL.min is an NA value fill with this value
                                          log1p(MDL.min))) %>% 
   dplyr::mutate(Year = Year - 1998) # We want to use years since 1998 

```

## Plot fish against sediments 

We will plot the fish DDT concentration against DDT concentration in sediment (faceted by feeding position).

```{r}
fish_reg %>% 
  dplyr::mutate(feeding_position = factor(feeding_position, 
                                          levels=c("Benthic","Benthopelagic","Midwater","Pelagic"))) %>% 
  ggplot(mapping=aes(x=TotalDDT.sed.trans, # ddt concentration in sediment 
                     y=TotalDDT.trans.non, # ddt concentration in fish
                     fill= trophic_category )) +
  geom_jitter(size=1.5, pch=21) +
  ylab("[DDXfish] ng/g lipid") +
  xlab("[DDXsed] ng/g dw") +
  facet_wrap(~feeding_position, nrow=1)+
  scale_fill_manual(values = c("#ffffcc","#a1dab4","#41b6c4","#225ea8"), name="Diet")+
  theme_bw() +
  theme(legend.position = "none")
```

## Some simple modeling 

To understand Bayesian modeling: https://www.r-bloggers.com/2019/05/bayesian-models-in-r-2/

## Run BRMS Models 

Run the models.

*What is the difference between the interactions (colon vs asterik)?*

```{r}
# Look at best structure for model 
brm.none = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans, 
               data = fish_reg, 
               prior = c(set_prior("cauchy(0, 0.5)", 
                                   class = "b")))

brm.habitat.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:feeding_position, 
                        data = fish_reg, 
                        prior = c(set_prior("cauchy(0, 0.5)", 
                                            class = "b")))

brm.habitat.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + feeding_position, 
                            data =  fish_reg, 
                            prior = c(set_prior("cauchy(0, 0.5)", 
                                                class = "b")))

brm.diet.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:trophic_category, 
                     data =fish_reg, 
                     prior = c(set_prior("cauchy(0, 0.5)", 
                                         class = "b")))

brm.diet.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + trophic_category, 
                         data =fish_reg, 
                         prior = c(set_prior("cauchy(0, 0.5)", 
                                             class = "b")))

brm.trophic = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category, 
                  data =fish_reg, 
                  prior = c(set_prior("cauchy(0, 0.5)", 
                                      class = "b")))

brm.habitat = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * feeding_position, 
                  data =fish_reg, 
                  prior = c(set_prior("cauchy(0, 0.5)", 
                                      class = "b")))

brm.diet.habitat = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position, 
                       data =fish_reg, 
                       prior = c(set_prior("cauchy(0, 0.5)", 
                                           class = "b")))

brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data =fish_reg, 
                            prior = c(set_prior("cauchy(0, 0.5)", 
                                                class = "b")))

brm.diet.habitat.species = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position  + (1|CompositeCommonName), 
                               data =fish_reg, 
                               prior = c(
                                 set_prior("cauchy(0, 0.5)", class = "b"),   
                                 set_prior("cauchy(0, 2)", class = "sd")))

brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data =fish_reg, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))
```


## Creating a function to add covariates 

### Next steps:

* Create function in order to add covariates and test models with ease

```{r}
update_models <- function(covariate) {
  fish_reg
  
}
```

