# Load Packages

```{r message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(tidymodels)
library(caret)
# Load the corrplot package
library(corrplot)
library(sjPlot)
library(rstanarm)

if("pacman" %in% installed.packages() == FALSE){install.packages("pacman")}
pacman::p_load(geojsonR, factoextra,sf,dplyr, ggplot2, maps, fields,raster, 
               MuMIn, lubridate, tidyr,ggh4x, lme4,sdmTMB,inlabru,cowplot,marmap,sjPlot, tidyverse, plyr, tidybayes, brms, bayesplot, loo,ggeffects,
               DHARMa)
```

# Set up with clean data

```{r, message = FALSE}
# load in the cleaned data with transformed variables 
fish_clean <- read_csv(here::here("data", "fish_clean.csv"))

# load in the life hsitory characteristics
fish_lh <- read_csv(here::here("data", "fish_data", "fish_life_history.csv"))

# Read in sediment data 
sediment_summary = readRDS(here::here("data","sediment_data","totalDDX_sediment_zone_summary.rds")) %>%
  dplyr::select(Name, Est.2003, Est.2008, Est.2013, Est.2018) %>% 
  gather(key="Year",value="TotalDDT",Est.2003:Est.2018) %>% 
  dplyr::mutate(Year = case_when(Year == "Est.2003" ~ "2003",
                                 Year == "Est.2008" ~ "2008",
                                 Year == "Est.2013" ~ "2013",
                                 Year == "Est.2018" ~ "2018")) %>% 
  dplyr::group_by(Name, Year) %>%
  dplyr::summarize(TotalDDT.sed = (mean((TotalDDT)))) %>%
  dplyr::ungroup() 

```

The life history characteristics of interest are the trophic level, trophic category, and the feeding position.

# Testing different models using Machine learning

## Split the data

```{r}
set.seed(425)
fish_split <- initial_split(fish_clean)
fish_train <- training(fish_split)
fish_test <- testing(fish_split)

```

## Load the models of interest

### Their model with `TotalDDT.trans` variable which is transformed DDT concentrations that have been lipid-normalized. This is the baseline accuracy that we are testing.

```{r}
fish_clean_original <- read_csv(here::here("data", "fish_clean_ORIGINAL.csv"))

brm.diet.habitat.species.year.original = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                      TotalDDT.sed.trans * feeding_position + Year +
                                      (1|CompositeCommonName), data = fish_clean_original,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")))

loo(brm.diet.habitat.species.year.original)
bayes_R2(brm.diet.habitat.species.year.original)

# make predictions
cvvs <- loo_predict(brm.diet.habitat.species.year.original)

fish_clean_original %>% 
  mutate(prediction = cvvs) %>% 
  ggplot(aes(x = TotalDDT.trans, 
                 y = prediction)) +
  geom_point() +
  geom_smooth(method = "glm")
```

### Prediction values

This will be the body of the function that predicts DDT concentrations using user inputs. Data will be drawn from life history dataframe, as well as possible sources for sediment concentration. /

Questions to consider:

\- How to read the output if the variables are logged?

\- Do we have to transform them so that they make sense?

\- Currently the output is a negative number, this doesn't feel like it makes sense.

\- When collecting samples, were the fish at maturity/ at fishing standard? If this is the case, then we could add a predictor variable of size, since there are laws that limit catch size and could inform DDT concentration.

```{r}
# Example output of specific DDT concentration using the model
predict(brm.diet.habitat.species.year.original, 
        data.frame(CompositeCommonName = "barred sand bass", # grab from df
                   TotalDDT.sed.trans = 0.009889753, # get from fishing zone
                   trophic_category = "Tertiary Carnivore", # get from life history characteristics
                   feeding_position = "Benthopelagic", # get from life history characteristics
                   Year = 2050))

fish_predict <- predict(brm.diet.habitat.species.year.original,
                        fish_test) %>% 
  bind_cols(fish_test)

ggplot(data = fish_predict) +
  geom_point(aes(x = TotalDDT.trans.non, y = Estimate))



```

### Our models with the `TotalDDT.trans.non` variable which is transformed DDT concentration, that has not been lipid normalized.

```{r}

# using species 
brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))

# removing species from the model 
brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_train, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")#,   
                              #set_prior("cauchy(0, 2)", class = "sd"))
                            ))


# with tropic level
brm.diet.habitat.tropic.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + tropic_level + Year, 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b")))

fish_train %>% 
  ggplot(aes(x = tropic_level, y = trophic_category)) +
  geom_point()
```

## Set up cross-validation to test model accuracy

```{r}
summary(brm.diet.habitat.species.year)
bayes_R2(brm.diet.habitat.species.year)
loo(brm.diet.habitat.species.year)

loo(brm.diet.habitat.species.year, 
    brm.diet.habitat.year, 
    brm.diet.habitat.tropic.year)
```

Perforn kfold cross validation on each model, and output the rmse.

```{r}

kf <- kfold(brm.diet.habitat.year, save_fits = TRUE, chains = 1)

# define a loss function
rmse <- function(y, yrep) {
yrep_mean <- colMeans(yrep)
sqrt(mean((yrep_mean - y)^2))
}

kfp <- kfold_predict(kf)
rmse(y = kfp$y, yrep = kfp$yrep)
```

### Select the model that performs the best

## Next steps

1.  We have confirmed the model that predicts the DDT concentration in fish based on life history characteristics
2.  Create function
