# Load Packages

```{r message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(tidymodels)
library(caret)
# Load the corrplot package
library(corrplot)
library(sjPlot)
library(rstanarm)

library(sf)
library(terra)
library(leaflet)

# if("pacman" %in% installed.packages() == FALSE){install.packages("pacman")}
# pacman::p_load(geojsonR, factoextra,sf,dplyr, ggplot2, maps, fields,raster, 
#                MuMIn, lubridate, tidyr,ggh4x, lme4,sdmTMB,inlabru,cowplot,marmap,sjPlot, tidyverse, plyr, tidybayes, brms, bayesplot, loo,ggeffects,
#                DHARMa)
```

# Set up with clean data

```{r, message = FALSE}
# load in the cleaned data with transformed variables 
fish_clean <- read_csv(here::here("data", "data_outputs", "fish_clean.csv"))

# load in the life hsitory characteristics
fish_lh <- read_csv(here::here("data", "fish_data", "fish_life_history.csv"))

# Read in sediment data 
sediment_summary = readRDS(here::here("data","sediment_data","totalDDX_sediment_zone_summary.rds")) %>%
  dplyr::select(Name, Est.2003, Est.2008, Est.2013, Est.2018) %>% 
  gather(key="Year",value="TotalDDT",Est.2003:Est.2018) %>% 
  dplyr::mutate(Year = case_when(Year == "Est.2003" ~ "2003",
                                 Year == "Est.2008" ~ "2008",
                                 Year == "Est.2013" ~ "2013",
                                 Year == "Est.2018" ~ "2018")) %>% 
  dplyr::group_by(Name, Year) %>%
  dplyr::summarize(TotalDDT.sed = (mean((TotalDDT)))) %>%
  dplyr::ungroup() 


```

```{r}
# Comparing the number of fish in the fish_clean and the fish_lh
fish_clean_names <- as.data.frame(unique(fish_clean$CompositeCommonName)) 

fish_lh_names <- as.data.frame(unique(fish_lh$species)) 

# what fish are in fish_lh that are not in the fish_clean
subset(fish_lh_names, 
       !(fish_lh$species %in% fish_clean$CompositeCommonName))


```

## Exploring length and weight variables
```{r}
# eploring the missing weight and length data 
null_weight_fish <- fish_clean %>% 
  filter(is.na(WeightAvg.g))

null_length_fish <- fish_clean %>% 
  filter(is.na(TLAvgLength.mm))

# names of unique ID's
fish_clean_names <- as.data.frame(unique(fish_clean$CompositeCompositeID)) 

# what fish are in null_weight_fish that are not in the null_length_fish
null_length <- subset(fish_clean_names, 
       !(null_weight_fish$CompositeCompositeID %in% null_length_fish$CompositeCompositeID))

null_length_df <- fish_clean %>% 
  filter(CompositeCompositeID %in% null_length$`unique(fish_clean$CompositeCompositeID)`)

null_w_l <- rbind(null_weight_fish, null_length_df)
```


The life history characteristics of interest are the trophic level, trophic category, and the feeding position.

# Testing different models using Machine learning

## Split the data

```{r}
set.seed(425)
fish_split <- initial_split(fish_clean)
fish_train <- training(fish_split)
fish_test <- testing(fish_split)

```

## Load the models of interest

### Their model with `TotalDDT.trans` variable which is transformed DDT concentrations that have been lipid-normalized. This is the baseline accuracy that we are testing.

```{r}
fish_clean_original <- read_csv(here::here("data", "data_outputs", "fish_clean_ORIGINAL.csv"))

brm.diet.habitat.species.year.original = brm(TotalDDT.trans|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
                                      TotalDDT.sed.trans * feeding_position + Year +
                                      (1|CompositeCommonName), data = fish_clean_original,
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),
                                      set_prior("cauchy(0, 2)", class = "sd")))

# using species 
brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data = fish_clean, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))

# removing species from the model 
brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_clean, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")#,   
                              #set_prior("cauchy(0, 2)", class = "sd"))
                            ))

loo_results <- LOO(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year,
                   brm.diet.habitat.year)

R2.results = lapply(X=list(brm.diet.habitat.species.year.original,
                   brm.diet.habitat.species.year,
                   brm.diet.habitat.year), 
                   FUN=bayes_R2)
R2.results

fish_predict <- predict(brm.diet.habitat.species.year.original,
                        fish_clean_original) %>% 
  bind_cols(fish_clean_original)

accuracy_vec(fish_predict, truth = TotalDDT.trans, estimate = Estimate)

# make predictions
#cvvs <- loo_predict(brm.diet.habitat.species.year.original)

fish_clean_original %>% 
  mutate(prediction = cvvs) %>% 
  ggplot(aes(x = TotalDDT.trans, 
                 y = prediction)) +
  geom_point() +
  geom_smooth(method = "glm")
```

### Prediction values

This will be the body of the function that predicts DDT concentrations using user inputs. Data will be drawn from life history dataframe, as well as possible sources for sediment concentration. /

Questions to consider:

\- How to read the output if the variables are logged?

\- Do we have to transform them so that they make sense?

\- Currently the output is a negative number, this doesn't feel like it makes sense.

\- When collecting samples, were the fish at maturity/ at fishing standard? If this is the case, then we could add a predictor variable of size, since there are laws that limit catch size and could inform DDT concentration.

```{r}
# Example output of specific DDT concentration using the model
predict(brm.diet.habitat.species.year.original, 
        data.frame(CompositeCommonName = "barred sand bass", # grab from df
                   TotalDDT.sed.trans = 0.009889753, # get from fishing zone
                   trophic_category = "Tertiary Carnivore", # get from life history characteristics
                   feeding_position = "Benthopelagic", # get from life history characteristics
                   Year = 2050))

fish_predict <- predict(brm.diet.habitat.species.year.original,
                        fish_test) %>% 
  bind_cols(fish_test)

ggplot(data = fish_predict) +
  geom_point(aes(x = TotalDDT.trans.non, y = Estimate))



```

### Our models with the `TotalDDT.trans.non` variable which is transformed DDT concentration, that has not been lipid normalized.

```{r}

# using species 
brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b"),   
                                      set_prior("cauchy(0, 2)", class = "sd")))

# removing species from the model 
brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
                            data = fish_train, 
                            prior = c(
                              set_prior("cauchy(0, 0.5)", class = "b")#,   
                              #set_prior("cauchy(0, 2)", class = "sd"))
                            ))


# with tropic level
brm.diet.habitat.tropic.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + tropic_level + Year, 
                                    data = fish_train, 
                                    prior = c(
                                      set_prior("cauchy(0, 0.5)", class = "b")))

fish_train %>% 
  ggplot(aes(x = tropic_level, y = trophic_category)) +
  geom_point()
```

## Machine Learning Attempt 
```{r}
set.seed(425)
fish_split_o <- initial_split(fish_clean_original)
fish_train_o <- training(fish_split_o)
fish_test_o <- testing(fish_split_o)

fit_stan_glm <- 
  stan_glmer(bf(TotalDDT.trans | cen_paired(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category +
             TotalDDT.sed.trans * feeding_position + Year +
             (1|CompositeCommonName)), data = fish_train_o, refresh = 0, seed = 505)

```


## Set up cross-validation to test model accuracy

```{r}
summary(brm.diet.habitat.species.year)
bayes_R2(brm.diet.habitat.species.year)
loo(brm.diet.habitat.species.year)

loo(brm.diet.habitat.species.year, 
    brm.diet.habitat.year, 
    brm.diet.habitat.tropic.year)
```

Perforn kfold cross validation on each model, and output the rmse.

```{r}

kf <- kfold(brm.diet.habitat.year, save_fits = TRUE, chains = 1)

# define a loss function
rmse <- function(y, yrep) {
yrep_mean <- colMeans(yrep)
sqrt(mean((yrep_mean - y)^2))
}

kfp <- kfold_predict(kf)
rmse(y = kfp$y, yrep = kfp$yrep)
```

### Select the model that performs the best

## Next steps

1.  We have confirmed the model that predicts the DDT concentration in fish based on life history characteristics
2.  Create function

```{r}
sed_2018 <- rast(here::here("data", "sediment_data", "sediment_rasters", "sediment_totalDDT_2003.grd"))
plot(sed_2018)

summ <- readRDS(here::here("data", "fish_data", "pelagic_nearshore_fish_zones.rds"))
plot(summ)

ddt_fish <- read_csv(here::here("data", "data_outputs", "fish_clean.csv")) %>%
  na.omit(Co) %>% 
  st_as_sf(coords = c("CompositeTargetLongitude", "CompositeTargetLatitude"), 
           crs = st_crs(summ))


leaflet() %>%  
  setView(lng = -118.7, lat = 33.5, zoom = 7.5) %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addGeoJSON(summ$geometry,
             color = "#CEE0EAFF",
             weight = 2,
             fillOpacity = 0.1,
             layerId = "Hi") %>% 
  addCircleMarkers(data = ddt_fish,
                   radius = ~6,
                   color = "pink",
                   stroke = FALSE, fillOpacity = 0.5)
  
```

# Exploring the {fishbase} package in r

Here is the documentation (link)[https://cran.r-project.org/web/packages/rfishbase/rfishbase.pdf]

Suggestions:
- use scientific name not common name since there are many matches

```{r}
library(rfishbase)

# get the unique species names - should be 61
species_name <- unique(fish_clean$scientific_name)

# look at the list of species using the names - these are different sizes
species_info <- species(species_list = species_name)
```

Compared the differences in the names:
- Embiotica jacksoni			
- Rhinobatos productus			
- Doryteuthis opalescens
```{r}
# Comparing the number of fish in the fish_clean and the fish_lh
fish_clean_names <- as.data.frame(unique(fish_clean$scientific_name)) %>% 
  rename(species = 'unique(fish_clean$scientific_name)')

fish_lh_names <- as.data.frame(unique(species_info$Species))

# what fish are in fish_clean_names that are not in the species_info
subset(fish_clean_names, 
       !(fish_clean_names$species %in% species_info$Species))
```

Recode them into the names that are included in fishbase 
- I couldn't find a record on the fishpase backage of Doryteuthis opalescens, but it has the family Loliginidae
```{r}
# update the names of the fish to match fishbase
species_name_clean <- as.data.frame(species_name) %>% 
  dplyr::mutate(species_name = case_when(species_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                         species_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                          TRUE ~ species_name))

# look at the taxa of the fish 
taxa <- rfishbase::load_taxa()

# filter the taxa based on name 
taxa_filter <- taxa %>% 
  filter(Species %in% species_name_clean$species_name) %>% 
  select(scientific_name = Species, Family, Genus)

fish_clean_test <- fish_clean %>% 
  left_join(taxa_filter, by = "scientific_name")
```

