---
title: "Hope Model Stuff"
author: "Hope Hahn"
date: "2024-02-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

set.seed(23)
```

## <span style="color: grey;">Overview</span>

---

### The Data

The data used in this project will be:

***Sediment Data***

The sediment .rds file contains the total DDT sediment concentration and year. 

***Fish Data***

Fish life history:
Fish life history data contains trophic and feeding position data for species that were sampled. 

Fish DDT data:
Fish DDT data contains total DDT concentration, lipid normalized DDT data, and other fish DDT information.

### Main Steps
***Client Code***

* Read in and tidy sediment and fish data
* Bayesian modeling using brms package

***My Code***

<<<<<<< HEAD
* ML attempt 1
* ML attempt 2
* ML attempt 3 (success)
* Splitting data by species
* Running models again using family instead of species

*Note*: At the bottom of each section, there is a summary of what problems I encountered, and what needs to be fixed/looked into moving forward. After looking through the code, read through this section before proceeding with updates.

### Summary of document

This file has been a continuous progress of applying tidymodels to the models. In the last section, I used the multilevelmod extension package to add family as a random effect. I will be continuing this process in the tidymodels_clean.Rmd file where I will run the models with species and family as both fixed and random effects.

## <span style="color: grey;">Code</span>

---

### Client Code

In this section, the necessary code from the client script is copied and pasted. Their modeling code is not pasted into a chunk to avoid running it accidentally since we will not need to run it here. It is just acting as a reference for my own code.

**Regress fish [DDT] against sediment [DDT]**

```{r}
# install and/or load the necessary R packages
if("pacman" %in% installed.packages() == FALSE){install.packages("pacman")}
pacman::p_load(geojsonR, factoextra,sf,dplyr, ggplot2, maps, fields,raster, 
               MuMIn, lubridate, tidyr,ggh4x, lme4,sdmTMB,inlabru,cowplot,marmap,sjPlot, tidyverse, plyr, tidybayes, brms, bayesplot, loo,ggeffects,
               DHARMa)
#rgeos, INLAutils, DHARMa.helpers)
```

**Load in data and add censoring column**

In these steps, we will read in the data, and combine relevent data. We will add columns of transformed data and add censoring column.

*What is censoring column?*

```{r}
fish_reg <- read.csv(here::here("data", "data_outputs", "fish_clean.csv"))
```

**Client BRMS models**

These are the client models. I will not put them into a code chunk.

*What is the difference between the interactions (colon vs asterik)?*

# -------------------------------
brm.habitat.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:feeding_position, 
data = fish_reg, 
prior = c(set_prior("cauchy(0, 0.5)", 
class = "b")))

brm.habitat.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + feeding_position, 
  data =  fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.diet.slope = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + TotalDDT.sed.trans:trophic_category, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.diet.intercept = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans + trophic_category, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.trophic = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.habitat = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * feeding_position, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.diet.habitat = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.diet.habitat.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year, 
  data =fish_reg, 
  prior = c(set_prior("cauchy(0, 0.5)", 
  class = "b")))

brm.diet.habitat.species = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position  + (1|CompositeCommonName), 
  data =fish_reg, 
  prior = c(
  set_prior("cauchy(0, 0.5)", class = "b"),   
  set_prior("cauchy(0, 2)", class = "sd")))

brm.diet.habitat.species.year = brm(TotalDDT.trans.non|cens(Censored, Detection.Limit) ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName), 
  data =fish_reg, 
  prior = c(
  set_prior("cauchy(0, 0.5)", class = "b"),   
  set_prior("cauchy(0, 2)", class = "sd")))
  
# -------------------------------

### My Code:

=======
* ML Attempt #1 - FAILED
* ML Attempt #2 - FAILED
* ML Attempt #3 - SUCCESS
* Adding random effects

*Note*: At the bottom of the page, there is a summary of what problems I encountered, and what needs to be fixed/looked into moving forward. After looking through the code, read through this section before proceeding with updates.

>>>>>>> e4baa05f8352564c634f50a3aa8735fd8c0ec066
This is a series of my code. I will be keeping code that has failed as well, but commenting out which lines do not run. Under this section, there will be a log of what went wrong, and what we need to fix moving forward.

#### ML attempt 1:

I will try to apply what we learned in ML labs 1 and 2 to see if we can use this for Bayesian regression.

**Prep:**
```{r}
library(tidyverse)
library(tidymodels)

# select only relevant columns
fish_cleaned <- read_csv(here::here("data", "data_outputs", "fish_clean.csv"))

# ------------------------------------- this didnt work ------------------------------
# set formula
## dont know how this would work with bayesian modeling
#fish_formula <- brmsformula(total_ddt_trans_non|cens(censored, detection_limit) ~ #total_ddt_sed_trans * trophic_category + total_ddt_sed_trans * feeding_position  + #(1|composite_common_name)) 
# ------------------------------------------------------------------------------------

# split training and testing data
fish_split <- fish_cleaned %>% 
  initial_split(prop = 0.7)

fish_train <- training(fish_split)
fish_test <- testing(fish_split)

# are we supposed to put the correct formula in here?? bc it does not work when copy and pasting above thing
# try out recipe: 
fish_recipe <- recipe(TotalDDT.trans.non ~ ., data = fish_train) %>% 
  step_integer(all_predictors(), zero_based = TRUE)

fish_prep <- prep(fish_recipe)

fish_baked <- bake(fish_prep, new_data = NULL)
```

**Setting and training the model**

```{r}
# set model specification
brm_fish_spec <- linear_reg() %>% 
  set_engine("stan", prior = c(
    set_prior("cauchy(0, 0.5)", class = "b"),   
    set_prior("cauchy(0, 2)", class = "sd"))) %>% 
  set_mode("regression")

# create workflow
brm_wf <- workflow() %>% 
  add_recipe(fish_recipe) %>% 
  add_model(brm_fish_spec) 

library('rstanarm')

# Train the model
## Commented this out for knitting ----
#brm_wf_fit <- brm_wf %>% 
  #fit(data = fish_train) 

# make predictions
#predictions <- brm_wf_fit %>% 
 # predict(new_data = fish_test)
```

### ML attempt 2:

The previous attempt did not work because of problems with setting the priors I believe. Trying it out again without adding priors.

```{r}
fish_recipe <- recipe(TotalDDT.trans.non ~ ., data = fish_train) %>% 
  step_integer(all_predictors(), zero_based = TRUE)

# set model specification
brm_fish_spec <- linear_reg() %>% 
  set_engine("stan") %>% # taking out priors for now
  set_mode("regression")

# create workflow
brm_wf <- workflow() %>% 
  add_recipe(fish_recipe) %>% 
  add_model(brm_fish_spec) 

# Train the model
brm_wf_fit <- brm_wf %>% 
  fit(data = fish_train) 

# make predictions
predictions <- brm_wf_fit %>% 
  predict(new_data = fish_test)
```


It worked, so the priors did appear to be the problem, need to figure out how to add priors to set_engine().

---

## Log/Summary:

* I first tried to apply their exact formula into the recipe, it didn't work so I just used "~." for the recipe.

* There are issues with the priors in the set_engine() function. We need to figure out how to input priors here. "priors =" is meant to be put in the set_engine, but they way they put it is with set_priors() which is brms package. With the priors, everything runs, up to fitting the model to the training data. 

* When we take priors out of set_engine(), we can fit the model to the training data and get predictions.

## Moving Forward Checklist

* How do we specify their exact formula in the recipe?

* What is the proper way to add priors into the set_engine() function?

* After we figure those out, we will need to cross-validate: Bruce mentioned trying LOO using tidymodels (there is a function) to see if we get the same accuracy as them, and we also wanted to try other methods I believe (k-fold CV?).

--- 

### ML attempt 3:

After the client meeting on 2/29, the clients said that it would be okay to remove the censored column. The | function is proper format for the BRMS package. I will remove that part and try again to see if it works.

Breaking up the steps:

**Setting a recipe**

Setting a recipe is setting instructions for pre-processing the data. The necessary preprosessing is converting all predictors to numeric.
"When using the formula method via fit(), parsnip will convert factor columns to indicators."

https://workflows.tidymodels.org/reference/add_formula.html

```{r}
#fish_recipe <- recipe(TotalDDT.trans.non ~ ., data = fish_train) %>% 
  #step_integer(all_predictors(), zero_based = TRUE) %>% 
```

**Setting model spec**

Added priors to this one. I added the class "b" prior from the client's model; I think the "sd" class was for the random group effects, and I took those out anyways.

```{r}
# set model specification
brm_fish_spec <- linear_reg() %>% 
  set_engine("stan", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")
```

**Create a workflow**

The new workflow will include the model spec as well as the formula.

I had to take out the censored thing and the species as a random effect.

```{r}
# create workflow 
brm_wf <- workflow() %>% 
  add_model(brm_fish_spec) %>% 
  add_formula(TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year)
```

**Resample and finalize wf**

Resampling with 10-fold CV, but I am not sure how to finalize workflow. Not sure what metric would be appropriate to use here.

```{r}
set.seed(23)

# create folds
folds <- vfold_cv(fish_train, v = 10)

# resample
fit_rs <- brm_wf %>% 
  fit_resamples(folds)

fit_rs$.metrics

# collect metrics
collect_metrics(fit_rs)
```

**Train model**

Fit the model to the train data and make predictions with the training data.

```{r}
# Train the model
brm_wf_fit <- brm_wf %>% 
  fit(data = fish_train) 

# make predictions
train_predict_brm <- predict(object = brm_wf_fit, new_data = fish_train) %>% #predict the training set
  bind_cols(fish_train)
```

**Fit to test data**

```{r}
test_predict_brm <- predict(brm_wf_fit, fish_test) %>% #get prediction probabilities for test data
  bind_cols(fish_test) #bind to testing column
```

**Accuracy and metrics**

```{r}
metrics(test_predict_brm, truth = TotalDDT.trans.non, estimate = .pred)

#accuracy(test_predict_brm, truth = TotalDDT.trans.non, estimate = predicted)
```

---

## Log/Summary:

* After some research, it appears that perhaps a recipe was not required, and when fitting the data, it automatically converts to integers with "stan". 

* Instead of setting a recipe, I set a formula. To get the model to fit to the data, I had to remove the censor column and species as a random effect.

## Moving Forward Checklist

* We need to figure out how to properly resample this data, and look into how to evaluate model accuracy.

* It would be cool to figure out a way to keep the censored data and species in the formula to test the tidymodels accuracy against the brms package.

* If we figure out how to keep the original formula, then we can use tidymodels LOO compared to the LOO they used. 

--- 

### Splitting the Data

```{r}
set.seed(23)

# Split the data into groups based on species
grouped_data <- fish_cleaned %>%
                group_split(CompositeCommonName)
# Create an empty list to store sampled dataframes
sampled_dataframes <- list()
# Loop through each group, sample 70% of data and store it in the list
for (group in grouped_data) {
  sampled_data <- group %>%
                  sample_frac(0.7, replace = FALSE)
  sampled_dataframes[[length(sampled_dataframes) + 1]] <- sampled_data

}
```

```{r}
set.seed(23)
distinct_species <- unique(fish_cleaned$scientific_name)

# Sample 70% of distinct species
sampled_species <- sample(distinct_species, size = 0.7 * length(distinct_species))
# Filter the original dataframe to retain only the rows corresponding to sampled species
train_data_unique <- fish_cleaned %>%
               filter(scientific_name %in% sampled_species)

test_data_unique <- fish_cleaned %>% 
  filter(!(scientific_name %in% sampled_species))
```

---

### Running models again using family instead of species

*This is Luna's code*

```{r}
library(rfishbase)

# get the unique species names - should be 61
species_name <- unique(fish_cleaned$scientific_name)

# look at the list of species using the names - these are different sizes
species_info <- species(species_list = species_name)

# update the names of the fish to match fishbase
species_name_clean <- as.data.frame(species_name) %>% 
  dplyr::mutate(species_name = case_when(species_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                         species_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                          TRUE ~ species_name))

# look at the taxa of the fish 
taxa <- rfishbase::load_taxa()

# filter the taxa based on name 
taxa_filter <- taxa %>% 
  filter(Species %in% species_name_clean$species_name) %>% 
  dplyr::select(scientific_name = Species, Family, Genus)

fish_clean_fam <- fish_cleaned %>% 
  dplyr::mutate(scientific_name = case_when(scientific_name == "Embiotica jacksoni" ~ "Embiotoca jacksoni",
                                            scientific_name ==  "Rhinobatos productus" ~ "Pseudobatos productus",
                                            TRUE ~ scientific_name)) %>%
  left_join(taxa_filter, by = "scientific_name") %>% 
  dplyr::mutate(Family = ifelse(scientific_name == "Doryteuthis opalescens",
                                "Loliginidae",
                                Family))
```

**Splitting the data by unique species**
- Adding this code chunk here with the updated species names
```{r}
set.seed(23)
distinct_species <- unique(fish_clean_fam$scientific_name)

# Sample 70% of distinct species
sampled_species <- sample(distinct_species, size = 0.7 * length(distinct_species))
# Filter the original dataframe to retain only the rows corresponding to sampled species
train_unique <- fish_clean_fam %>%
               filter(scientific_name %in% sampled_species)

test_unique <- fish_clean_fam %>% 
  filter(!(scientific_name %in% sampled_species))

print(sort(unique(train_unique$Family)))
print(sort(unique(test_unique$Family)))
```
*Now this is my code again*

```{r}
# split new data
fam_split <- initial_split(fish_clean_fam, prop = 0.7)
fam_train <- training(fam_split)
fam_test <- testing(fam_split)

species_split <- initial_split(fish_cleaned, prop = 0.7)
species_train <- training(species_split)
species_test <- testing(species_split)
```

I am trying a new way based on multilevelmod documentation

```{r}
library(multilevelmod)
# create spec
brm_fish_spec_fam <- linear_reg() %>% 
  set_engine("stan_glmer", 
             prior_intercept = rstanarm::cauchy(0, 0.5)) %>%
  set_mode("regression")

# create workflow
###THIS ONE DID NOT WORK!!!
#fam_wflow <- 
  #workflow() %>% 
  #add_model(brm_fish_spec_fam) %>% 
  #add_formula(TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|Family))

# this is the workflow suggested by multilevelmod 
# I will try it to see if i get same results
lmer_wflow <- 
  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, Family)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|Family))

# species workflow
species_wf <-  workflow() %>% 
  add_variables(outcomes = TotalDDT.trans.non, predictors = c(TotalDDT.sed.trans, trophic_category, TotalDDT.sed.trans, feeding_position, Year, CompositeCommonName)) %>% 
  add_model(brm_fish_spec_fam, formula = TotalDDT.trans.non ~ TotalDDT.sed.trans * trophic_category + TotalDDT.sed.trans * feeding_position + Year + (1|CompositeCommonName))
```

**Fit the workflows to the split training and testing data**

```{r}
# Train the model
#brm_fam_fit <- fam_wflow %>% 
  #fit(data = fam_train) 

# This first workflow did not work

# train using the other workflow
brm_fam_fit2 <- lmer_wflow %>% 
  fit(data = fam_train) 

brm_species_fit <- species_wf %>% 
  fit(data = species_train)

# Fit the workflows to the split by unique species
brm_fam_unique <- lmer_wflow %>% 
  fit(data = train_unique)
```

Run the models on the testing data:

```{r}
# predict using other workflow
test_predict_fam2 <- predict(brm_fam_fit2, fam_test) %>% #get prediction probabilities for test data
  bind_cols(fam_test)

test_predict_species <- predict(brm_species_fit, species_test) %>% 
  bind_cols(species_test)

# predict using other workflow
test_predict_unique <- predict(brm_fam_unique, test_unique) %>% #get prediction probabilities for test data
  bind_cols(test_unique)
```

---

## Log/Summary

* I used the split data that isolated the species and the model had a worse rmse than the two below that used 
- Luna

---

```{r}
# test accuracy
metrics(test_predict_fam2, truth = TotalDDT.trans.non, estimate = .pred)

metrics(test_predict_species, truth = TotalDDT.trans.non, estimate = .pred)

metrics(test_predict_unique, truth = TotalDDT.trans.non, estimate = .pred)
```
**Create table for each of the models**
Luna code again

```{r}
library(sjPlot)

fam_mod <- tab_df(metrics(test_predict_fam2, truth = TotalDDT.trans.non, estimate = .pred))
species_mod <- tab_df(metrics(test_predict_species, truth = TotalDDT.trans.non, estimate = .pred))
species_split_mod <- tab_df(metrics(test_predict_unique, truth = TotalDDT.trans.non, estimate = .pred))

species_mod
fam_mod
species_split_mod
```

---

## Log/Summary

* I used the parsnip extension package called multilevelmod to add family and species as a random effect. 

* Model performed better with species as a random effect vs family as a random effect.

* Now that we've figured out random effects in tidymodels, what about adding censoring??

* Tables are printed above

---
